\message{ !name(resume.tex)}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[hidelinks]{deedy-resume-openfont}
\usepackage{fancyhdr}
\renewcommand{\sectionsep}[0]{\vspace{8pt}} 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

\message{ !name(resume.tex) !offset(-3) }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Rihan}{Pereira}{
    \urlstyle{same}\href{https://rihbyne.github.io}{rihbyne.github.io}
  | \href{mailto:rihen234@gmail.com}{rihen234@gmail.com}
  | +919545236646
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Mumbai University}
\descript{BE in Information Technology}
\location{July 2010-2014 | Mumbai, MH} 
St. Francis College of Engineering \\
\location{Avg. 55\%}
\sectionsep

\subsection{Thomas Batista J College}
\descript{grade-12(Science)}
\location{Feb 2010 | Mumbai, MH}
\location{Avg. 72\%}
\sectionsep

\subsection{St. Augustine High School}
\descript{grade-10}
\location{March 2008 | Mumbai, MH}
\location{Avg. 76\%}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Facebook:// \href{https://facebook.com/rihenp}{\custombold{rihenp}} \\
GitHub:// \href{https://github.com/rihbyne}{\custombold{rihbyne}} \\
YouTube:// \href{https://www.youtube.com/c/RihanPereira}{\custombold{RihanPereira}} \\
Twitter:// \href{https://twitter.com/rihbyne}{\custombold{@rihbyne}} \\
soundcloud:// \href{http://www.soundcloud.com/rihbyne}{\custombold{@rihan}} \\
Quora://  \href{https://www.quora.com/Rihan-Pereira}{\custombold{Rihan-Pereira}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
Intro. to Computer Programming\\
Data Structures and Algorithms\\ 
Object-Oriented Programming\\
Operating Systems\\
Computer Networks and  Security\\
Database and Storage Management
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Extensive:}
Python \textbullet{} Javascript \textbullet{} Unix  \textbullet{} Git \\
emacs \\
\location{Comfortable:}
Java \textbullet{}  Ant \textbullet{} Django \textbullet{} SQL \\ SSHs \\
\location{Familiar:}
React.js \textbullet{} Node.js
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Hackathons
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{ACHIEVEMENTS}
\begin{tabular}{rll}
1\textsuperscript{st}/10 & Inter-Class Music, Dec-2007\\
1\textsuperscript{st}/13 & Inter-Class Music, Nov-2006\\
2\textsuperscript{nd}/5 & Inter-Class Art, Aug-2004\\
3\textsuperscript{rd}/6 & 4x100 Mts. Relay,Sports Dec-2004 \\
2\textsuperscript{nd}/6 & 4x100 Mts. Relay,Sports Dec-2002
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%79\% in ``Developing your Musicianship'' coursera MooC \\

%Instrumental Music(Dec 2007)
%1\textsuperscript{st}/10 Inter-Class Competition\\

%Instrumental Music(Nov. 2006
%1\textsuperscript{st}/13 Inter-Class Competition\\

%2\textsuperscript{st}/5 Inter-Class Art Competition


%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Aasaanjobs}
\descript{| Software Development Engineer}
\location{Dec 2014 – June 2015 | Mumbai}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item  Excercised acquired understanding of DVS tool \custombold{Git}, learned to resolve merge conflicts, branching,hotfixes, stash, git-flow.
\item Deflated codebase while refactoring and wrting responsive static UI.
\item  Worked on a feature to implement user-facing design to handle CRUD
operations which consume json using MVC Design Pattern.
\item Applied understanding of Python/Django MVC,used Django\'s built-in ORM to write
  aggregate queries for a module's View.
\item An assignment to port a small portion of existing jquery code to AngularJS.
\end{tightemize}
\sectionsep

\runsubsection{Global Point Solutions}
\descript{| Software Engineering Intern}
\location{ Jan 2013 - March 2013 | Mumbai}
\begin{tightemize}
\item Worked with frontend team to design and improve UI using \custombold{js} and Bootstrap framework.
\end{tightemize}
\sectionsep

\runsubsection{Google Summer of Code 2013}
\descript{| project participant}
\location{April 2013 – June 2013 | Google Melange |
  link:-> \href{http://www.google-melange.com/gsoc/proposal/public/google/gsoc2013/rihnapstor/5707702298738688}{project draft}}
\begin{tightemize}
\item Drafted a technical project prosopal about automating bug reporting
  for participating organization \href{http://code.timvideos.us/home/}{\custombold{Tim Videos}}.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Home Automation System API}
\descript{}
\location{Feb 2014 – April 2014 |
  \href{https://github.com/rihbyne/app_control_client}{rihbyne/HA-app} | \href{https://github.com/rihbyne/control_server_api}{rihbyne/control-servo}}
\begin{tightemize}
\item This project implementation was inspired from Internet of Things(m2m)
  concept.It makes use of Open Source hardware, Raspberry Pi.
\item The request routing logic is written on top of Express middleware
  framework and deployed on \custombold{Node.js }application server running on
  Raspberry Pi.
\item The logic is then exposed as REST like web service endpoint which is then
  invoked from a Web-app/Command-Line(CLI) app.
\end{tightemize}
\sectionsep

\runsubsection{BeatBox}
\descript{}
\location{Sep 2013 | \href{https://github.com/rihbyne/BeatBox}{rihbyne/Beatbox}}
\begin{tightemize}
\item Beatbox is a Java Swing GUI program.It has 16x16 checkbox grid.It makes
  use of java MIDI library to generate eclectic sound patterns.
\item Loops over checked checkboxes on different sound patterns.
\item The app can save/restore patterns state and adjust tempo as well.
\end{tightemize}
\sectionsep

\runsubsection{Simple  Quiz}
\descript{}
\location{Sep 2013 | \href{https://github.com/rihbyne/Quiz-form}{rihbyne/Quiz-form}}
\begin{tightemize}
\item Simple Quiz is a web-based UI quiz written in js, xhtml, css.It notifies
  the correct choice for wrong solution and accordingly increments the score.
\end{tightemize}
\sectionsep

\runsubsection{Theatre Movie Booking System}
\descript{}
\begin{tightemize}
\item This program is windows Standalone Desktop App that I created as part of
 coursework during my sophomore year of Undergraduation. 
%\item This system takes user through a wizard to help select a movie generating
 %detailing user opted choices.
\item This program demonstrates the following:\\
  - use of for-loop for seat reservation.\\
  - Display seat status considering empty to total seats.\\
  - Establish connection to MS-SQL and generate detail report on user choices.
\end{tightemize}
\sectionsep




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%     Other
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\section{Other}
%
%\runsubsection{Zimm's Yard Services}
%\descript{| Owner}
%\location{May 2008 – Aug 2013 | New Berlin, WI}
%\begin{tightemize}
%\item Started neighborhood lawn service business, ran for five summers
%\item Developed \custombold{Java} app to track transactions, create invoices,
%  etc.
%\end{tightemize}
%\sectionsep

%\runsubsection{SDNB Tech Dept}
%\descript{| Intern }
%\location{Jun 2013 – Aug 2013 | New Berlin, WI}
%\begin{tightemize}
%\item Aided with common IT-related tasks, such as batch OS imaging \& BIOS editing
%\item Provided technical and troubleshooting support for faculty and staff
%\end{tightemize}
%\sectionsep

%\runsubsection{Kumon Learning Center}
%\descript{| Math and Reading Tutor}
%\location{Oct 2011 – Aug 2013 | Franklin, WI}
%\begin{tightemize}
%\item Tutored math and reading one-on-one with students aged pre-K to high school
%\end{tightemize}
%\sectionsep

%\runsubsection{Spanish Language Interpreter}
%\descript{| Ebenezer Food Pantry}
%\location{2009 - 2013 | Milwaukee, WI}
%\sectionsep
%\runsubsection{Student Tech Speaker}
%\descript{| Bring Your Own Device Talk Series}
%\location{2012 - 2013| Wisconsin}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% NOTE: These are not mine. They are remnants from the template.
%  \section{Awards}
%  \begin{tabular}{rll}
%  2014	     & top 52/2500  & KPCB Engineering Fellow\\
%  2014	     & 2\textsuperscript{nd} most points  & Google Code Jam, Qualification Round\\
%  2014	     & 1\textsuperscript{st}/50  & Microsoft Coding Competition, Cornell\\
%  2013	     & National  & Jump Trading Challenge Finalist\\
%  2013     & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament  \\
%  2012     & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot Tournament \\
%  2011     & National & Indian National Mathematics Olympiad (INMO) Finalist \\
%  2010     & National & Comp. Soc. of India's National Programming Contest\\
%  \end{tabular}
%  \sectionsep
%
%  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  %     SOCIETIES
%  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  \section{Societies}
%
%  \begin{tabular}{rll}
%  2014 	& top 12\%ile    & Tau Beta Pi Engineering Honor Society\\
%  2014   & National   & The Global Leadership and Education Forum (tGELF)\\
%  2012   &  National  & Golden Key International Honor Society\\
%  2012   &  National   & National Society of Collegiate Scholars\\
%  \end{tabular}
%  \sectionsep
%
\end{minipage}
\end{document}  \documentclass[]{article}

\message{ !name(resume.tex) !offset(-325) }
