%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}

%\renewcommand{\sectionsep}[0]{\vspace{8pt}}

\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Rihan}{Pereira}{
    \urlstyle{same}\href{http://swlogs.me/}{swlogs.me}
  | \href{mailto:rihen234@gmail.com}{rihen234@gmail.com}
  | +919545236646
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Mumbai University}
\descript{BE in Information Technology}
\location{July 2010-2014 | Mumbai, MH} 
St. Francis College of Engineering
\sectionsep

\subsection{Thomas Batista J College}
\descript{grade-12(Science)}
\location{Feb 2010 | Mumbai, MH}
\sectionsep

\subsection{St. Augustine High School}
\descript{grade-10}
\location{March 2008 | Mumbai, MH}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
blog:// \href{http://swlogs.me/blog}{\bf swlogs.me/blog} \\
Projects:// \href{http://swlogs.me/DIY}{\bf swlogs.me/DIY} \\
github:// \href{https://github.com/rihbyne}{\bf rihbyne} \\
goodreads://  \href{https://goodreads.com/rihbyne}{\bf goodreads.com/rihbyne} \\ 
soundcloud:// \href{http://www.soundcloud.com/rihbyne}{\bf @rihan} \\
%youTube:// \href{https://www.youtube.com/c/RihanPereira}{\custombold{RihanPereira}} \\
quora://  \href{https://www.quora.com/Rihan-Pereira}{\bf Rihan-Pereira}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
Intro. to Computer Science\\
Data Structures and Algorithms\\ 
Object-Oriented Design and Principles\\
Operating Systems\\
Cryptography \\
Computer Networks \\
Database and Storage Management \\
Software Testing and Quality Assurance
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Tools \& Programming}
\location{Extensive:}
Nodejs \textbullet{} Python \textbullet{} Javascript \textbullet{} Unix \\
Git/svn \textbullet{} Emacs \\
\location{Comfortable:}
Java \textbullet{} NoSQL \textbullet{} SQL \\
\location{Familiar:}
Memcache 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Hackathons
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{ACHIEVEMENTS}
\begin{tabular}{rll}
  2017 & 3x & Top Performer recognition\\
  & & in Bitstreet's newsletter\\
  2007 & 1\textsuperscript{st}/10 & Inter-Class Music\\
  2006 & 1\textsuperscript{st}/13 & Inter-Class Music\\
  2004 & 2\textsuperscript{nd}/5 & Inter-Class Art\\
  2004 & 3\textsuperscript{rd}/6 & 4x100 Mts. Relay\\
  2002 & 2\textsuperscript{nd}/6 & 4x100 Mts. Relay
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%79\% in ``Developing your Musicianship'' coursera MooC \\

%Instrumental Music(Dec 2007)
%1\textsuperscript{st}/10 Inter-Class Competition\\

%Instrumental Music(Nov. 2006
%1\textsuperscript{st}/13 Inter-Class Competition\\

%2\textsuperscript{st}/5 Inter-Class Art Competition


%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Bitstreet Technologies}
\descript{| Software Developer}
\location{Jan 2016 – present | Mumbai}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item  Solid exposure in logical and persistence tier of their multi-tier
  architecture. Currently involved in the development of Wallet as a Service(WaaS)
  which plugs in all types of crypto-currencies.
\item Code management lead. Encouraged use of \textbf{Git-flow} among teammates.
\item Defined APIs for 2FA Integration.
\item Secured user accounts using \href{http://swlogs.me/blog/user-auth/}{\textbf{salting \& hashing}} technique.
\item Became familiar with and thereafter used  \href{http://swlogs.me/blog/hmac-authentication/}{\textbf{HMAC Authentication \& Signature Verification}} applied to API calls.
\item Studied \& implemented \href{http://swlogs.me/DIY/nonce-auth-systems/}{\textbf{Crytographic Nonce}}
  as a middleware in logical tier as a defense against replay attacks.
\item Developed code to enable stateless cursor based pagination API at scale, spanning data over multiple
  collections. Packaged it into portable library as it was reused twice in different application context in production.
\item Used \href{http://swlogs.me/DIY/multi-tenancy/}{\textbf{software multitenancy}} on application server to share common set of resources among different merchants using (Role-based Access Control)RBAC and database isolation.
\item Documented project module workings and manual test cases.
\end{tightemize}
\sectionsep

\runsubsection{Aasaanjobs}
\descript{| Software Development Engineer III}
\location{Dec 2014 – July 2015 | Mumbai}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item  Excercised acquired understanding of DVCS tool Git, learned to resolve
  merge conflicts, branching, hotfixes, stash, git-flow.
\item Refactored and wrote new responsive UI.
\item Wrote Javascript code to handle CRUD endpoints and maniputate it for dynamic UI experience.
\item Applied understanding of Python/Django's MVC \& ActiveRecords.
\item wrote python/js scripts to perform database cleanups and automate notifications triggering.
\end{tightemize}
\sectionsep



%\runsubsection{Global Point Solutions}
%\descript{| Software Engineering Intern}
%\location{ Jan 2013 - March 2013 | Mumbai}
%\begin{tightemize}
%\item Worked with frontend team to design and improve UI using JS, HTML5, CSS, Grid Layout .
%\end{tightemize}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects \& Articles}
\runsubsection{The Moneypot project}
\descript{| case study}
\location{March 2016 – April 2016}
\begin{tightemize}
\item Contract project \href{http://swlogs.me/blog/the-moneypot-project/}{\textbf{moneypot.com}} undertaken on
  behalf of my firm to analysis \& borrow its web system internals.
\item open/closed bugs on issue tracker.

\end{tightemize}
\sectionsep

\runsubsection{Electrical Appliance control \& Integration}
\descript{}
\location{Feb 2014 – April 2014}
\begin{tightemize}
\item Senior year undergraduation application project inspired from Internet of Things(IoT),
  machine to machine(M2M) concept.
\item Reading data through sensors, driving appliances interfaced to Raspberry Pi.
\item Developed end user monitoring and control panel - a daemon, WebUI, and command-line.
\end{tightemize}
\sectionsep

\runsubsection{TimVideos.us}
\descript{}
\location{April 2013 – June 2013 }
\begin{tightemize}
\item A proposal submitted as part of GSOC 2013 which articulates implementation
  details for one of the many project ideas
  \href{http://swlogs.me/blog/gsoc-2013/}{\textbf{Bug Reporting tool}}.
\end{tightemize}
\sectionsep
%\runsubsection{BeatBox}
%\descript{}
%\location{Sep 2013 | \href{https://github.com/rihbyne/BeatBox}{rihbyne/Beatbox}}
%\begin{tightemize}
%\item Beatbox is a Java Swing GUI program.It has 16x16 checkbox grid.It makes
%  use of java MIDI library to generate eclectic sound patterns.
%\item Loops over checked checkboxes on different sound patterns.
%\item The app can save/restore patterns state and adjust tempo as well.
%\end{tightemize}
%\sectionsep
%
%\runsubsection{QA Quiz}
%\descript{}
%\location{Sep 2013 | \href{https://github.com/rihbyne/Quiz-form}{rihbyne/Quiz-form}}
%\begin{tightemize}
%\item QnA Quiz is a web-based UI quiz written in js, xhtml, css.It notifies
%  the correct choice for wrong solution and accordingly increments the score.
%\end{tightemize}
%\sectionsep

%\runsubsection{Theatre Movie Booking System}
%\descript{}
%\begin{tightemize}
%\item This program is windows Standalone Desktop App that I created as part of
% coursework during my sophomore year of Undergraduation. 
%%\item This system takes user through a wizard to help select a movie generating
% %detailing user opted choices.
%\item This program demonstrates the following:\\
%  - Event handlers, display seat status considering empty to total seats.\\
%  - Establish connection to MS-SQL DB and generate ticket on user choices.
%\end{tightemize}
%\sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}
