% LaTeX source of my resume
% =========================

% This file is licensed under the CC-NC-ND Creative Commons license.

% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume-single-column}
\newcommand{\quotes}[1]{``#1''}

\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Rihan Pereira}{}{}
%{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:rihen234.at.gmail.dot.com}{rihen234\mbox{}@\mbox{}gmail.com}\sbull
\textsmaller{+}1.805.444.9850\sbull
\href{https://rihbyne.github.io}{rihbyne.github.io}\sbull
\href{https://linkedin.com/in/rihbyne/}{linkedin.com/in/rihbyne/}
% \\
% Mathenesserplein 84\sbull
% 3022\thinspace {\large \sc ld}\sbull
% Rotterdam\sbull
% The Netherlands

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

%\roottitle{Summary}  % a root section title
%
%\vspace{-1.3em}  % some vertical spacing
%\begin{multicols}{2}  % open a multicolumn environment
%\noindent \emph{Entrepeneurial spirit and geek god with roots in the open source movement. Passionately enabling software-related teams to deliver. Creates/\,structures/\,improves processes. Architects and helps to implement future-proof solutions. Coaches both individuals and groups.}
%\\
%\\
%At the age of seven (1989) Cies wrote his first lines of code in a \acr{LOGO}-like language on an \acr{MSX} (pre-\acr{PC}).  Two years later he attended a conference on an emerging new technology, the Internet, at the Erasmus University from which he would graduate 16 years later (2000) with a degree in Business Computer Science.
%
%After being introduced to the open source movement in 1997, he taught himself a variety of skills including system administration and programming (Bash, Python, Ruby \& \CPP).  By 2002 he got his pet project \acr{KT}urtle ---a zero-entry-barrier programming environment--- included in \acr{KDE}'s \emph{edu} module, and thereby in almost every Linux distribution.
%
%Extensively travelled Europe and Asia after graduating. On return his professional life became a mix of hands-on work in startups and web software agencies, while settling as a husband and father in personal life.
%\end{multicols}


%\spacedhrule{0em}{-0.4em}

\roottitle{Experience}

%\headedsection
%% \href{https://addons.mozilla.org/en-US/firefox/}{mozilla.addons.org}
%{\textscale{0.9}{\textbf{Open Source developer}}}
%  {\textsc{Remote}}
%  {%
%    \headedsubsection
%    {}
%    {Aug 2018 -- present}
%    {
%      \begin{itemize}
%        \item Contributing code to \href{https://www.softwaredaily.com/}{Software Daily} android repository.
%        \item Fixing \href{https://wiki.mozilla.org/Add-ons/Contribute/Recognition\#August_2018}{good-first-bugs} of \href{https://addons.mozilla.org/en-US/firefox/}{mozilla.addons.org} project.
%      \end{itemize}
%    }
%  }

\headedsection
  {\href{http://bitstreet.in/}{Bitstreet Technologies}}
  {\textsc{Mumbai, India}}
  {%
    \headedsubsection
    {Software Developer}
    {Jan 2016 -- Dec, 2017}
    {
      \begin{itemize}
        \item Managed multiple repositories. Encouraged use of \textbf{Git-flow} design among team of 4 developers.
        \item Contributions in logical and persistence tier, bitcoin(BTC) gateway integration, setup experimental bitcoin cash(BCH) \href{https://rihbyne.github.io/diy/digital-wallet/}{\textbf{wallet app}} end-to-end, batch process transaction metadata.
        \item Secured user accounts using \href{https://rihbyne.github.io/blog/user-auth/}{\textbf{salting \& hashing}} technique and Multi-factor Authentication(2FA) with backup \& recovery options.
        \item \href{https://rihbyne.github.io/blog/hmac-authentication/}{\textbf{HMAC \& Signing}} applied to JSON-REST/RPC API calls.
        \item Studied \& implemented \href{https://rihbyne.github.io/diy/nonce-auth-systems/}{\textbf{Nonce}} as an addition to secure message passing between internal services as a defense against replay attacks.
        \item Developed stateless cursor based \href{https://rihbyne.github.io/diy/stateless-pagination/}{\textbf{pagination API}} at scale, spanning data over multiple MongoDB \href{https://rihbyne.github.io/diy/notification-core/}{\textbf{collections}}(\textit{was reused twice in different application context in production}).
        \item Used \href{https://rihbyne.github.io/diy/multi-tenancy/}{\textbf{software multitenancy}} on application server to share common set of resources among different tenants using (Role-based Access Control)RBAC and database isolation.
        \item Produced supportive documentation and designed system diagrams.
      \end{itemize}
    }
  }

\headedsection
    {\href{https://www.aasaanjobs.com/}{Aasaanjobs}}
    {\textsc{Mumbai, India}}
    {%
      \headedsubsection
      {Software Development Engineer I}
      {Dec 2014 -- July 2015}
      {
        \begin{itemize}
          \item Hands-on git, exercised git-flow workflow design, learned to resolve merge conflicts, branching, hotfixes, stash, interactive rebase.
          \item Refactored and wrote new responsive UI.
          \item Wrote Javascript code to handle REST endpoints and maniputate it for dynamic UI experience.
          \item Wrote automated UI tests using PhantomJS - headless browser environment.
          \item Write python/js scripts to execute database backups, traverse spreadsheet data to fanout notifications.
        \end{itemize}
      }
    }

\vspace{-0.2em}
\begin{center}
  \emph{\small I maintain my list of active and past projects at \href{http://rihbyne.github.io/diy}{rihbyne.github.io/diy} .}
\end{center}


\spacedhrule{-0.2em}{-0.4em}

\roottitle{Education}

\headedsection
  {\href{https://www.csuci.edu/}{California State University, Channel Islands}}
  {\textsc{California, U.S.A}} {%
  \headedsubsection
    {Master of Science(M.S) in Computer Science}
    {Jan 2018 -- Dec 2019(expected)}
    {
      \begin{itemize}
        \item Presented `\textit{Macaroons as better web cookies}` as part of COMP 524 Security class
        \item Presented `\textit{Scalable Web Architectures(SWA)}` as part of COMP 599 Graduate Seminar
        \item Produced a report on `\textit{Image Segmentation methods}` as part of COMP 510 Adv. Image Analysis Techniques
        \item Compiled a report on `\textit{Financial Analysis between Heineken vs Boston Beer}` as part of BUS 504 Finance \& Accounting class
        \item resolved a small UI patch under \href{https://wiki.mozilla.org/Add-ons/Contribute/Recognition\#August_2018}{good-first-bugs} of \href{https://addons.mozilla.org/en-US/firefox/}{mozilla.addons.org} project.
        \item Sketched a interactive \href{https://github.com/rihbyne/watch-ml-behave}{dashboard} as part of COMP 549 HCI class using python-tkinter GUI lib/flask, which integrates an existing handwritten recognition neural network, allows to load/configure/save versions of it. 
        \item Implemented CBC mode to systematically encrypt/decrypt a large plaintext file using 16 rounds of 64-bit DES.
      \end{itemize}
    }
  }

\headedsection
  {\href{http://www.mu.ac.in/}{Mumbai University, St. Francis Institute of Technology}}
  {\textsc{Mumbai, India}} {%
  \headedsubsection
    {Bachelor of Engineering(B.S) in Information Technology}
    {June 2010 -- May 2014}
    {
      \begin{itemize}
        \item Senior year project on data-driven IoT application using nodeJS/expressJS/raspberrypi
      \end{itemize}
    }
}

\spacedhrule{0.5em}{-0.4em}

\roottitle{Skills}

% \inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
\inlineheadedsection
{\textbf{Tools \& Programming:}}
{Knows Python/\nsp Javascript/\nsp Node.js} and Java. Semantic HTML5/CSS3. Emacs user. Experience writing secure REST APIs in Django/Flask/Expess.js. Familiar with Memcached, MongoDB, MySQLDB(e.g indexing, schema migrations). Enjoys challenges to architect and implement scalable web applications. Linux Power User. Well versed with Git.

%{
%  \headedsubsection
%  {Extensive}
%  {} {%
%    \begin{itemize}
%    \item c
%    \item d
%    \end{itemize}
%  }
%  
%  \headedsubsection
%  {Familiar}
%  {} {%
%    \begin{itemize}
%    \item a
%    \item b
%    \end{itemize}
%  }
%}

\spacedhrule{1.6em}{-0.4em}

\roottitle{Achievements}
{%
    \begin{itemize}
    \item Awarded and recognized as a \quotes{Top Performer}, \quotes{Best Performing Team}, \quotes{Meeting Expectations Plus Performance} for the year 2017 at {\href{http://bitstreet.in/}{Bitstreet Technologies}}.
    \end{itemize}
}

\end{document}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
